Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-26 answer-to-reviewers.tex

\emph{We agree with Reviewer~2 that such a sketch is helpful, and now provide two such sketches in Figure~2.}

\item Even though the use of the zero sub-indexed double struck capital N is correct for positive naturals and zero, I think that the simpler double struck capital N is enough. The context makes evident the inclusion of zero.

\smallskip

\emph{By using $\naturals_0$ and not $\naturals$ as suggested by Reviewer 2,
we intended to emphasize that the system RLD is evaluated for the first time directly at system startup time 0,
and thus prefer to keep using $\naturals_0$.}

@@

\emph{Thanks for pointing this out, done.}

\item Frequent references to function $g$, which is only defined later in Section 5.2, make the lecture of the manuscript difficult. I suggest to rewrite the section seeking for all elements to be introduced in a more orderly fashion.

\smallskip

\emph{Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
and to explain the details of its calculation later.
In the rewritten Section~5, we now mention this more explicitely.}

@@

\section*{Reviewer 3}

The paper is well structured, well written and technically accurate. The numerical experiments are particularly interesting. I recommend the acceptation of the paper after a revision.

The weak point of the work is related to the different hypothesis which significantly simplify the modeling framework. More precisely:

\emph{In the revision of our manuscript, we have aimed to emphasize the pilot character of our approach,
which should be seen as a first step towards a completely new class of CBM policies.
We now discuss these and other restricting assumptions more prominently in the Introduction, Section~5, and in the conclusion (Section~8).}

@@

\emph{In the revision of our manuscript, we have aimed to emphasize the pilot character of our approach,
which should be seen as a first step towards a completely new class of CBM policies.
We now discuss these and other restricting assumptions more prominently in the Introduction, Section~5, and in the conclusion (Section~8).}

\begin{enumerate}
\item All the components have the same lifetime model (namely the Weibull distribution) with a known fixed shape parameter which is not discussed. Only the scale parameter is updated and directly associated with the mean lifetime if the shape parameter is known.

\smallskip

\emph{Yes, each component type has an individual Weibull model assigned,
where the (component type specific) shape parameter is assumed to be fixed and known.
We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
We have added a comment on this in the conclusion,
repeating a comment from the beginning of Section~4, where we wrote:
``The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by Soland (1969).''
We now also emphasize in the introduction and the conclusion that the method as described in the manuscript is deliberately kept simple
to allow for a clear and straight-forward demonstration of the general approach.
For a practical application, one should indeed update the shape parameter as well,
but in our view, adding this conceptually simple but notationally cumbersome feature would obstruct the goal of this manuscript.}

@@

\item In the introduction the authors claim that ``the system RLD does not require a physical inspection’’ because the failure time of each component is detected online via continuous monitoring. This hypothesis seems to be very strong as it requires a costly related instrumentation. Most of the time, systems with redundancies are not monitored in a such way. if a specific application field is inferred, please give it explicitly. It could be interesting to discuss shortly the sensitivity of the proposed maintenance policy to non-detection of some components failures.

\smallskip

\emph{We have added a short discussion related to the non-detection of component failures in the conclusion.
We were mostly thinking of systems where a failure of a component is immediately eminent,
but the measurement of the component's health degree is very difficult or too costly.
This is, e.g., the case for components in power systems, where failure of a certain component
is usually reflected in a loss of current (detectable from the control centre),
but proper health monitoring (going beyond working yes/no) is cumbersome and costly.}

@@

\item The maintenance of the system is always a replacement of the whole system by an as good as new one. This hypothesis is hard to accept especially if all the components are continuously monitored.

\smallskip

\emph{In the rewritten Section~5, we discuss this point now extensively in Section~5.2:
``At first sight, replacing a complete system when only some parts of it are defective may seem strange.
However, there are many real life examples, including from daily life.
So called complete clustering (Olde Keizer et al, 2017)
may be optimal in case of a very strong economic dependence between the different parts of a system,
e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done,
as is the case of installations used in the generation and distribution of oil and gas.
Note that often for safety reasons, the latter installations are monitored continuously.
There may be also technical dependencies between parts of a system that may require combined replacement:
replacing the cassette of a bike often also requires to replace the chain,
and the tires of an airplane are required to have the same thickness.
But also complete systems are replaced because replacing one or more of its parts may take much longer,
which may result in big production losses.
Another reason can be that there may be a high probability that when individual parts are replaced,
other parts will be damaged, requiring their replacement as well.''}
\end{enumerate}

@@

Some additional comments or remarks are given hereafter to help improving the paper.

\begin{enumerate}
\item The literature review has a strong focus on papers that are very close to the proposed one. There are some ambiguities about what the authors call ``papers having some relation to their approach’’. For example the paper by Si et al. (2013) is referred first as a paper where the inspection of the system condition lead to the choice of the moment for the next inspection. There are a lot of (older) papers with that specificity. The reason why Si et al.~(2013) has been chosen is probably the RUL update in a Bayesian framework. It is not clear at this stage.

\smallskip

\emph{We did mention right in the first paragraph of the discussion of Si et al.~(2013)
that they use an empirical Bayesian framework,
but we now also state explicitely that the use of a Bayesian approach is a main reason why we consider this paper relevant for the discussion.}

@@

\item Page 1, last line: Maintaining systems or components at the right time is the central idea of all the maintenance policies, not only for CBM. The specificity of CBM is to take the decision about maintenance on the basis of the on-line system condition.

\smallskip

\emph{Agreed. We now give a better definition of CBM, as
``using information about the actual condition of the systems or components''.}

@@

\item Page 2, line 18 from top: The phrase ``a kind of inspection-based CBM policy’’ is maladjusted. The paper does not deal with inspection. The system is supposed to be continuously monitored (and re-evaluated from times to times). It would also be interesting to give in details the specific points which make the proposed policy a ``kind of’’ CBM policy.

\smallskip

\emph{Agreed, we deleted that notion, and hope to be more clear now here.}

@@

\emph{Agreed, the respective sections are now added.}

\item Page 7: The choice of the inverse Gamma distribution as a prior is interesting for mathematical reasons. Are there some possible tests to justify this choice from data?

\smallskip

\emph{It is not possible to use data for testing the adequacy of the parametric family of the prior,
as it is supposed to reflect the expert's opinion.
So the crucial question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
A tool to help answering that question are prior predictive distributions.
They give a distribution for the failure times that can be expected according to the expert's choice of prior
(here: inverse Gamma with specific parameters)
\textbf{in combination with the assumed sample model} (here: Weibull).
Figure~6 (previously Figure~5) depicts prior predictive reliability functions for the priors in the case study of Section~6,
as a way to visualize the choice of prior parameters given in Table~2 in the context of the Weibull model.
When an expert feels that these prior predictive reliability functions do not correspond to the failure time distribution (s)he postulates,
and no change of prior parameters can approximate the postulated failure time distribution,
then the prior family would seem inappropriate,
under the condition that the sample model is indeed correct.
We now briefly discuss this issue in Section~6.1,
also giving a reference to methods for checking the correctness of the sampling model.}

@@

\item Page 13, section 5.1: The grid of planned evaluation time points is defined with a ``sufficiently small’’ time increment. What does it mean quantitatively? It seems that if $\delta$ is very small the maintenance time will be almost given by $\tau_*^{(\tnow)}$.

\smallskip

\emph{We have completely rewritten Section~5 and now address the role of $\delta$ in more detail there, as well as in the Introduction.}

@@

\item Page 14, first paragraph: Is it possible to determine the number of operational cycles which is necessary to improve significantly the values of the parameters? It seems that after a certain amount of time the updates will have a negligible effect.

\smallskip

\emph{Indeed, due to the weigthed average update in Equation (7),
it is possible that the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
will not change by much once it has approached the 'true' value.
However, the strength parameter $n_k$ will continue to increase,
since the other part of (7) reads $n'_k = n_k + e_k$, i.e.,
$n_k$ is incremented by 1 for each observed failure.
The consequence is that the posterior distribution over $\lambda_k$ becomes ever more pointed
(the variance of the posterior approaches zero),
such that the posterior predictive distribution approaches the Weibull distribution with $\lambda_k$ equal to $y_k$.
Stopping to update would make only sense when the posterior is practically equal to a point mass on $y_k$.
However, this holds only if a component's failure behaviour does not change.
Updating allows to automatically adapt to any changes in the failure behaviour.}

@@

\item Page 14, Equation (14): Is it possible to have some elements about the variance of the unit cost rate?

\smallskip

\emph{In Equation~(15), the unit cost rate $\gnow(\tau)$ is defined as
$\gnow(\tau) = \E[g(\tau \mid \Tsysnow)]$,
i.e., as expectation of the conditioned unit cost rate $g(\tau \mid \Tsysnow)$ from Equation~(14).
We do not think the variance of the conditioned unit cost rate,
$\text{V}[g(\tau \mid \Tsysnow)]$ is instructive for the purposes of our manuscript.}

@@

\item Page 15, line 12 from bottom: Please replace ``the costs rate’’ [sic!] by ``the mean cost rate’’.

\smallskip

\emph{We wrote ``$\gnow(\tau)$ gives the cost rate that we expect to incur [...]'',
which includes the notion of mean via ``expect'', and we hope this is clear enough.}
\end{enumerate}

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 5 and done

The cost-optimal moment of replacement for the system is obtained by minimizing
the expected cost rate per unit of time.
The unit cost rate is recalculated when components fail
or at the end of every (very short) fixed inter-monitoring*** interval,
leading to a dynamic maintenance policy,
since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
Via numerical experiments, some insight into the performance of the policy is given.
\end{abstract}

@@

Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in the Conclusion (Section~\ref{sec:outlook}).
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.

@@

The expected component failure behaviour obtained by the parameter choices in Table~\ref{tab:priorparams}
is visualized in Figure~\ref{fig:compprior1fig1},
showing the prior predictive reliability function for a single component of each type.
Note that these functions are not plain Weibull reliability functions,
but weighted averages over Weibull reliability functions according to the prior distribution over the scale parameter $\lambda_k$.
We see that, e.g., the median prior expected failure times are
$2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
While it is a priori quite unlikely that any type $C$ component will survive past time $6$,
we expect 25\% of type $H$ components to survive past time $10$.

@@

%A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
We conducted a small simulation study to illustrate the performance of our policy
as compared to corrective and age-based policies.
To be able to discern the effect of parameter learning over several operational cycles,
we simulated component failure times for five subsequent operational cycles for each simulation repetition.
We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
with policies that do not update component parameters at the end of an operational cycle.
We also distinguish the condition-based maintenance policies with and without continuous parameter update
as in Section~\ref{sec:examples}.
In total, we compare the six maintenance policies listed in Table~\ref{tab:sim-abbrev},
which also gives the abbreviations used in Figures~\ref{fig:br1sim1fig5Tt01}, \ref{fig:br1sim2fig5Tt01} and \ref{fig:br1sim3fig5Tt01}.

@@

Here, most condition-based and all age-based policies cannot avoid system failures entirely.
Both CBM-epu and CBM-npu result in one system failure in the $20 \times 5 = 100$ system runs,
whereas the two age-based policies each result in ten system failures.
System runtimes are less variable for the age-based policies
since they do not use the current system structure information, %available information on the component level,
i.e., which components have failed and which not. %during operational cycles
System runtimes are more variable for the condition-based policies,
but longer on average, leading to lower realized cost rates.
Again, CBM-cpu performs slightly better than CBM-epu
as it has the possibility to learn within an operational cycle as well,
managing to avoid system failures entirely. 
Still, CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
This confirms the observation from Section~\ref{sec:ex-3}
that current system structure information delivers a major part of the gains for our CBM policy.

@@

There are several aspects in our modelling that warrant further investigation.
In this paper, we assume that component failure times are observed precisely via monitoring.
However, in many applications, the component status can only be determined
at inspections, leading to interval-censored failure time observations.
Extending the model to account for interval-censored failure times
would allow to derive a condition-based maintenance policy with wider-spaced inspections,
which could also determine the optimal moment for the next inspection of the system.
%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
%we would need to add interval-censored data (failure has happened between last and current inspection)

@@

Another promising extension would be to use sets of conjugate priors for the component models.
This approach is described in \cite{2016:walter-coolen},
resulting in sets of residual life distributions $\Rsysnow(t)$,
%Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
The determination of the (set of) optimal time(s) to maintenance $\tausnow$
is then non-trivial,
and would involve decision criteria discussed in the imprecise probability literature,
like E-admissibility, maximality, or maximin \citep[see, e.g., \S 8][]{itip}.

@@

Gero Walter was supported by the DINALOG project CAMPI
(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').

Both authors would like to thank Frank Coolen for inspiring discussions
and valuable hints on maintenance optimization criteria.

>>>>

The cost-optimal moment of replacement for the system is obtained by minimizing
the expected cost rate per unit of time.
The unit cost rate is recalculated when components fail
or at the end of every (very short) fixed inter-evaluation interval,
leading to a dynamic maintenance policy,
since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
Via numerical experiments, some insight into the performance of the policy is given.
\end{abstract}

@@

Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in the conclusion (Section~\ref{sec:outlook}).
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.

@@

The expected component failure behaviour obtained by the parameter choices in Table~\ref{tab:priorparams}
is visualized in Figure~\ref{fig:compprior1fig1},
showing the prior predictive reliability function for a single component of each type.
Note that these functions are not plain Weibull reliability functions,
but weighted averages over Weibull reliability functions according to the prior distribution over the scale parameter $\lambda_k$.
Judging the adequacy of the prior parameter choices thus requires the sampling model to be correct.
Methods for checking the sampling model are discussed, e.g., in \citet{2000:bayarri-berger}.
Figure~\ref{fig:compprior1fig1} indicates that, e.g., the median prior expected failure times are
$2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
While it is a priori quite unlikely that any type $C$ component will survive past time $6$,
we expect 25\% of type $H$ components to survive past time $10$.

@@

%A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
We conducted a small simulation study to illustrate the performance of our policy
as compared to corrective and age-based policies.
To be able to discern the effect of parameter learning over several operational cycles,
we simulated component failure times for five subsequent operational cycles for each simulation repetition.
We thus can compare policies that use information gained in previous operational cycles
%We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
with policies that do not update component parameters at the end of an operational cycle.
We also distinguish condition-based maintenance policies with and without continuous parameter update
as in Section~\ref{sec:examples}.
In total, we compare the six maintenance policies listed in Table~\ref{tab:sim-abbrev},
which also gives the abbreviations used in Figures~\ref{fig:br1sim1fig5Tt01}, \ref{fig:br1sim2fig5Tt01} and \ref{fig:br1sim3fig5Tt01}.

@@

%Here, most condition-based and all age-based policies cannot avoid system failures entirely.
Here, only CBM-cpu can avoid system failures entirely.
Both CBM-epu and CBM-npu result in one system failure in the $20 \times 5 = 100$ system runs,
whereas the two age-based policies each result in ten system failures.
System runtimes are less variable for the age-based policies
since they do not use the current system structure information, %available information on the component level,
i.e., which components have failed and which not. %during operational cycles
System runtimes are more variable for the condition-based policies,
but longer on average, leading to lower realized cost rates.
Again, CBM-cpu performs slightly better than CBM-epu
as it has the possibility to learn within an operational cycle as well,
managing to avoid system failures entirely. 
Still, CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
This confirms the observation from Section~\ref{sec:ex-3}
that current system structure information delivers a major part of the gains for our CBM policy.

@@

There are several aspects in our modelling that warrant further investigation.
In this paper, we assume that component failure times are observed precisely via monitoring.
However, in many applications, the component status can only be determined
at inspections, leading to interval-censored failure time observations.
Extending the model to account for interval-censored failure times
would allow to derive a condition-based maintenance policy with wider-spaced inspections
by determining the optimal moment for the next inspection of the system.
%which could also determine the optimal moment for the next inspection of the system.
%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
%we would need to add interval-censored data (failure has happened between last and current inspection)

@@

Another promising extension would be to use sets of conjugate priors for the component models.
This approach is described in \cite{2016:walter-coolen},
leading to sets of residual life distributions $\Rsysnow(t)$.
Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
%and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
The determination of the (set of) optimal time(s) to maintenance $\tausnow$
is then non-trivial,
and would involve decision criteria discussed in the imprecise probability literature,
like E-admissibility, maximality, or maximin \citep[see, e.g., \S 8][]{itip}.

@@

Gero Walter was supported by the DINALOG project CAMPI
(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
%
Both authors would like to thank Frank Coolen for inspiring discussions
and valuable hints on maintenance optimization criteria.
